An efficient composition of bidirectional programs by tupling and lazy updates

### 2019-12-03 paper/4.xpg.tex
tiny

The first equality is simply based on the definitions of $pg$, $\putbxinline{Skip \ h}$ and $\getbxinline{Skip \ h}$. The second one tuples two results of $put$ and $get$ in the body of the if-expression. This is a trick since in some cases, the result of $pg$ may be undefined although there is no undefined when evaluating $\getbxinline{Skip \ h}$. The last equality is relatively oblivious.

@@

The problem for $cpg$ lies in redundant computation during evaluating. For keeping away such computations, we introduce an extension named $kpg$. While $cpg$ evaluates values eagerly, $kpg$ does the opposite. Every values are evaluated lazily in a computation of $kpg$. The input of $\kpginline{bx}$ is expanded to a 6-tuple $(ks, kv, ks', kv', s, v)$ where $ks$ and $kv$ keep the modification information same as $cpg$, $s$ and $v$ hold evaluated values, and $ks'$ and $kv'$ are used for lazy evaluation of actual values. The output of this function is also a 6-tuple $(ks, kv, ks', kv', s, v)$.\\
Suppose that we have a source $s_0$ and a view $v_0$. The pair of the updated source and view $(s, v)$ where $s = \putbx{bx}{s_0}{v_0}$ and $v = \getbx{bx}{s_0}$ can be obtained using $kpg$ as follows:

@@

In $kpg$, basically, functions for the updates will be kept in $ks'$ and $kv'$.
$\kpginline{Skip}$ and $\kpginline{Case}$ are special cases, because they require the actual values for evaluation. Therefore we evaluate the values by application of $ks' \ s$ and $kv' \ v$ and update $ks'$ and $kv'$ with the identity functions.
%Except $\kpginline{Skip}$ and $\kpginline{Case}$ where $s$ and $v$ hold actual values, functions for the computation will be kept in $ks'$ and $kv'$.
When evaluating $\kpginline{bx_1 \circ bx_2}$, $\underline{ks_1'}$ and $\underline{s_1}$ in the result of the first assignment are still redundant but they are not evaluated.

>>>>

The first equality is simply based on the definitions of $pg$, $\putbxinline{Skip \ h}$ and $\getbxinline{Skip \ h}$. The second one tuples two results of $put$ and $get$ in the body of the if-expression. This is a trick since in some cases, the result of $pg$ may be undefined although there is no undefined when evaluating $\getbxinline{Skip \ h}$. The last equality is relatively obvious.

@@

The problem for $cpg$ lies in redundant computations during evaluating. For keeping away such computations, we introduce an extension named $kpg$. While $cpg$ evaluates values eagerly, $kpg$ does the opposite. Every values are evaluated lazily in a computation of $kpg$. The input of $\kpginline{bx}$ is expanded to a 6-tuple $(ks, kv, ks', kv', s, v)$ where $ks$ and $kv$ keep the modification information same as $cpg$, $s$ and $v$ hold evaluated values, and $ks'$ and $kv'$ are used for lazy evaluation of actual values. The output of this function is also a 6-tuple $(ks, kv, ks', kv', s, v)$.\\
Suppose that we have a source $s_0$ and a view $v_0$. The pair of the updated source and view $(s, v)$ where $s = \putbx{bx}{s_0}{v_0}$ and $v = \getbx{bx}{s_0}$ can be obtained using $kpg$ as follows:

@@

In $kpg$, basically, functions for the updates will be kept in $ks'$ and $kv'$.
$\kpginline{Skip}$ and $\kpginline{Case}$ are special cases, because they require the actual values for evaluation. Therefore we evaluate the values by application of $ks' \ s$ and $kv' \ v$ and update $ks'$ and $kv'$ with the identity functions.
%Except $\kpginline{Skip}$ and $\kpginline{Case}$ where $s$ and $v$ hold actual values, functions for the computation will be kept in $ks'$ and $kv'$.
When evaluating $\kpginline{bx_1 \circ bx_2}$, $\underline{ks_1'}$ and $\underline{s_1}$ in the result of the first assignment are still redundant but not evaluated.
